\Large \bf Conjure: Summoning Proxies from Unused Address Space

### 2019-02-16 paper/paper.tex
Placement
Conclusion
Fix broken ref

However, there are proposals to encrypt the SNI in the Client Hello~\cite{esni},
though none have been implemented or deployed as of early 2019. Nonetheless,
if widely adopted, Encrypted SNI (ESNI) would offer a powerful solution for
\scheme applications by allowing the domain to remain hidden from the censor.
While the censor could still try to actively probe with guesses for the SNI,
servers could respond with generic ``Unknown SNI'' errors. If such responses
were common for incorrect SNI, the censor's efforts to identify phantom hosts
would be frustrated.

@@

\FigUpload

\FigDownload

@@

@@

\section{Future Work}
% 0.5 page

@@

\section{Conclusion}
%.25 page

\TODO{Write (0.25 page}

>>>>

However, there are proposals to encrypt the SNI in the Client Hello~\cite{ietf-tls-esni-02},
though none have been implemented or deployed as of early 2019. Nonetheless,
if widely adopted, Encrypted SNI (ESNI) would offer a powerful solution for
\scheme applications by allowing the domain to remain hidden from the censor.
While the censor could still try to actively probe with guesses for the SNI,
servers could respond with generic ``Unknown SNI'' errors. If such responses
were common for incorrect SNI, the censor's efforts to identify phantom hosts
would be frustrated.

@@

@@

\FigUpload
\FigDownload

@@

\section{Conclusion and Future Work}
% 0.5 page

@@

%\section{Conclusion}
%.25 page

%\TODO{Write (0.25 page}
